Submission

### 2021-05-10 code/Submission.Rmd
new additions

#### 2. How much have you heard or read about the development of automated facial recognition technology that can identify someone based on a picture or video that includes their face
```{r FACE2_Likert, echo=echoval, message=FALSE}
pew %>% filter(FACE1_W49 != "Refused") %>% ggplot(aes(x = groupKnow, fill = FACE1_W49)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Dark2") +
  labs(
    title = "Respondent's Familiarity With Facial Recognition",
    y = "Counts",
    x = "Literacy Category",
    fill = "How Much The Respondent\nKnows About Facial Recognition",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

@@

### Additional Tables For Key Figure 1
```{r KF1-tables, echo=echoval}
#Simple simple table of counts
KF1_T1 <- table(pew$sumRTBF, pew$publicDataNum) #public data should be private = 0
colnames(KF1_T1) = c("Public Data Should Be Private","Public Data Should Be Public")

@@

NOTE: NEED TO CREATE AND INCLUDE ALT. VERSION OF KEY FIGURE IN THIS SECTION

```{r}

>>>>

#### 2. How much have you heard or read about the development of automated facial recognition technology that can identify someone based on a picture or video that includes their face

```{r FACE2_Likert, echo=echoval, message=FALSE}
pew %>% filter(FACE1_W49 != "Refused") %>% ggplot(aes(x = groupKnow, fill = FACE1_W49)) +
  geom_bar(position = 'dodge', color = 'black') +
  scale_fill_brewer(palette = "Dark2") +
  labs(
    title = "Respondent's Familiarity With Facial Recognition",
    y = "Counts",
    x = "Literacy Category",
    fill = "How Much The Respondent\nKnows About Facial Recognition",
    caption = "Data sourced from\n2019 PEW American Trends Panel\nSurvey on Social Media Usage and\nPerceptions of Digital Privacy"
  ) +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))
```

@@

### Additional Tables For Key Figure 1
```{r KF1-tables, echo=echoval}
#Simple simple table of counts
KF1_T1 <- table(pew$sumRTBF, pew$publicDataNum) #public data should be private = 0
colnames(KF1_T1) = c("Data Should Be Private","Data Should Be Public")

KF1_T1 <- as.data.frame(KF1_T1)

KF1_T1 <- KF1_T1 %>% rename(
  "sumRTBF" = "Var1",
  "Stance On RTBF" = "Var2",
)

@@

### Distribution of Work

Jake and Adriana are best of friends and have split the work evenly. [PLACEHOLDER].

```{r, echo=F, message=FALSE}
